 

### 2021-02-01 vertical-thermal-review.Rmd
remove PAR- T_air gradients figure
#31

# DISPLAY ITEMS  (limit 8) # This chunk is for auto numbering of tables/figures
#figures
fig_schematic = 1
fig_NEON_vertical =  2
fig_NEON_differences  = 3
fig_leaf_T = 4
fig_treerings= 5 #not sure if we want to include one

@@

**Here we review how the biophysical environment and biological form and function vary across the vertical canopy gradient in forests.** 
We focus on five key themes (Fig. `r fig_schematic`):
(1) the biophysical environment;
(2) the leaf traits that most strongly influence leaf temperature and metabolism;
(3) resulting leaf temperature ($T_{leaf}$) and
(4) foliar metabolism, including stomatal conductance, photosynthesis, respiration, and volatile organic compound (VOC) production; and 
(5) resultant size-structuring of whole-tree and ecosystem function.
We then consider the implications for modeling /  climate change responses.

@@

![**Figure `r fig_NEON_differences`. Relationship of PAR differences between canopy and understory to air temperature buffering (a) across sites and (b) through time within a single site.** From NEON data. Current placeholder figure is Nidhi's first rough analysis. See [issue 31](https://github.com/EcoClimLab/vertical-thermal-review/issues/31). ](NEON_height_profiles/figures/differences_across_forests_temp.png)

@@

The strength of this buffering varies across forests, influenced by both forest characteristics (Fig. `r fig_NEON_differences`) and the biophysical environment.
First, buffering increases with canopy cover and water availability.
* greater cover --> lower max T and VPD, higher minT  [@davis_microclimatic_2019]
* greater cover -->  lower max T and light availability [@zellweger_seasonal_2019]
* [@thom_effects_2020; Tymen et al. 2017 ; Jucker et al. 2018 ; Hardwick et al. 2015] 
The omega factor (McNaughton and Jarvis, 1983; Jarvis & McNaughton 1986) describes the degree of aerodynamic coupling between the vegetation and the atmospheric boundary layer; the lower the value of omega, the greater the coupling.
"I wonder whether it would be useful to introduce such 'formal' terms used to describe what is essentially the same as buffering effect of canopies.
I'd have to read up some more to see if there are papers showing what sort of canopy characteristics influence omega.

>>>>

# DISPLAY ITEMS  (limit 8) # This chunk is for auto numbering of tables/figures
#figures
fig_schematic = 1
fig_NEON_vertical =  2
#fig_NEON_differences (issue #31)
fig_leaf_T = 3
fig_treerings= 4 #not sure if we want to include one

@@

**Here we review how the biophysical environment and biological form and function vary across the vertical canopy gradient in forests.** 
We focus on five key themes (Fig. `r fig_schematic`):
(1) the biophysical environment;
(2) the leaf traits that most strongly influence leaf temperature and metabolism;
(3) resulting leaf temperature ($T_{leaf}$) and
(4) foliar metabolism, including stomatal conductance, photosynthesis, respiration, and volatile organic compound (VOC) production; and 
(5) resultant size-structuring of whole-tree and ecosystem function.
*We then consider the implications for modeling /  climate change responses.*

@@

@@

The strength of this buffering varies across forests, influenced by both forest characteristics and the biophysical environment.
First, buffering increases with canopy cover and water availability.
* greater cover --> lower max T and VPD, higher minT  [@davis_microclimatic_2019]
* greater cover -->  lower max T and light availability [@zellweger_seasonal_2019]
* [@thom_effects_2020; Tymen et al. 2017 ; Jucker et al. 2018 ; Hardwick et al. 2015] 
The omega factor (McNaughton and Jarvis, 1983; Jarvis & McNaughton 1986) describes the degree of aerodynamic coupling between the vegetation and the atmospheric boundary layer; the lower the value of omega, the greater the coupling.
"I wonder whether it would be useful to introduce such 'formal' terms used to describe what is essentially the same as buffering effect of canopies.
I'd have to read up some more to see if there are papers showing what sort of canopy characteristics influence omega.
